---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ROCpower

<!-- badges: start -->
<!-- badges: end -->

The goal of ROCpower is to examine the sample sizes required to conduct the NHST, Minimum-effect tests, and equivalence tests for Receiver Operating Characteristic curves

## Installation

You can install the development version of ROCpower like so:

``` r
install_github("PaulRiesthuis/ROCpower")
```

## Example single ROC curve


To visualize the full or partial ROC curves and AUCs for parameters of interest
```{r, message=FALSE, warning=FALSE}
library(ROCpower)
# For single curve, use group1 parameters.
# Visualize full ROC curves and AUCs. n_g1 is intentionally large to have precise estimates. rho doesnt affect the AUC.
visualize_full_roc(mean_signal_g1 = 1, mean_signal_g2 = 0.58,
                   n_studied = 5, n_new = 5,
                   n_g1 = 10000,
                   sd_signal_g1 = 1, sd_signal_g2 = 1,
                   sd_noise_g1 = 1, sd_noise_g2 = 1,
                   mean_noise_g1 = 0, mean_noise_g2 = 0,
                   rho = 0, seed = 2794)

# Visualize partial ROC curves and AUCs. n_g1 is intentionally large to have precise estimates. rho doesnt affect the AUC.
visualize_partial_roc(mean_signal_g1 = 1, mean_signal_g2 = 0.58,
                   n_studied = 5, n_new = 5,
                   n_g1 = 10000,
                   sd_signal_g1 = 1, sd_signal_g2 = 1,
                   sd_noise_g1 = 1, sd_noise_g2 = 1,
                   mean_noise_g1 = 0, mean_noise_g2 = 0,
                   pauc = c(.63,.50),
                   rho = 0, seed = 2794)
```


To run a power analsysis for a single ROC curve
```{r, message=FALSE, warning=FALSE}
library(ROCpower)
## basic example code. Adjust the means and sds to get the ROC/AUC of interest.
simulate_single_roc(mean_signal = 0.34, mean_noise = 0,
                    sd_signal = 1, sd_noise = 1,
                    n_g = 100, n_studied = 5, n_new = 5,
                    n_simulations = 1000, SESOI = 0.55, seed = 2794)
```

## Example power analysis for difference between full ROC curves 

To run a power analysis for difference between full ROC curves 
```{r, message=FALSE, warning=FALSE}
library(ROCpower)
## basic example code. Adjust the means, sds, sample sizes for each group, and the correlation to get the ROC/AUC of interest.
simulate_two_roc(mean_signal_g1 = 1, mean_signal_g2 = 0.58,
                 mean_noise_g1 = 0, mean_noise_g2 = 0,
                 sd_signal_g1 = 1, sd_signal_g2 = 1,
                 sd_noise_g1 = 1, sd_noise_g2 = 1,
                 n_g1 = 100, n_g2 = 100,
                 n_studied = 5, n_new = 5,
                 n_simulations = 1000, SESOI = 0.05,
                 paired = FALSE, rho = 0.5, seed = 2794)
```

## Example power analysis for difference between partial ROC curves 

To run a power analysis for difference between partial ROC curves 
```{r, message=FALSE, warning=FALSE}
library(ROCpower)
## basic example code. Adjust the means, sds, sample sizes for each group, and the correlation to get the ROC/AUC of interest.
simulate_two_partial_roc(mean_signal_g1 = 1, mean_signal_g2 = 0.58,
                         mean_noise_g1 = 0, mean_noise_g2 = 0,
                         sd_signal_g1 = 1, sd_signal_g2 = 1,
                         sd_noise_g1 = 1, sd_noise_g2 = 1,
                         n_g1 = 100, n_g2 = 100,
                         n_studied = 5, n_new = 5,
                         pauc = c(.63,.50),
                         n_simulations = 3, SESOI = 0.05,
                         paired = FALSE, rho = 0.5, seed = 2794)
  
```
